\chapter{EXPERIMENT VERIFICATION AND TESTING}

\section{Verification Matrix}

\begin{longtable}{L{0.7cm}L{5cm}L{1.5cm}L{2cm}L{2.5cm}L{2cm}}
\caption{Verification Matrix}
\label{tab:verification_matrix} \\

\toprule
\textbf{ID} & \textbf{Requirement text} & \textbf{Method} & \textbf{Reference} & \textbf{Status} & \textbf{Verification Result} \\
\midrule
\endfirsthead

\multicolumn{6}{c}{\tablename\ \thetable\ -- \textit{Continued from previous page}}\\
\toprule
\textbf{ID} & \textbf{Requirement text} & \textbf{Method} & \textbf{Reference} & \textbf{Status} & \textbf{Verification Result} \\
\midrule
\endhead

\midrule
\multicolumn{6}{r}{\textit{Continued on next page}}\\
\endfoot

\bottomrule
\endlastfoot

F.1. & The experiment shall measure the atmospheric CH\textsubscript{4}, CO\textsubscript{2} and H\textsubscript{2}O concentrations of ambient air simultaneously with an off-the-shelf \gls{ndir} sensor. & R, T & Test 4, Test 14 & To be done (June) & Pending \\
F.2. & The measurement chamber shall be pressurised with ambient air. & R, T & Test 3 & To be done (June) & Pending \\
F.3. & The air in the measurement chamber shall be exchanged. & R,T & Test 3, Test 4 & To be done (earliest test in June) & Pending \\
F.4. & The experiment shall measure pressure inside of the measurement chamber. & R,T & Test 3, Test 8 & To be done (earliest test in June) & Pending \\
F.5. & The experiment shall measure the temperature inside of the measurement chamber. & R,T & Test 4, Test 9  & To be done (earliest test in June) & Pending \\
F.6. & The experiment shall stabilize the temperature inside the measurement chamber. & A,T & Test 6, Test 9 & To be done (earliest test in June) & Pending \\
F.7. & The experiment shall measure the humidity inside of the measurement chamber. & R,T & Test 4, Test 13 & To be done (earliest test in June) & Pending \\
F.8 & The experiment shall prevent the condensation of water inside the measurement chamber. & R, T & Test 13 & To be done (July) & Pending \\
F.9. & The experiment shall protect electronics from undercooling or overheating. & A, T & Test 6, Test 9 & To be done (earliest test in June) & Pending\\
F.10. & The experiment should measure ambient temperature outside. & R,T & Test 14 & To be done (August) & Pending \\
F.11. & The experiment should measure ambient pressure outside. & R,T &  Test 8, Test 14 & To be done (earliest in July) & Pending \\
F.12. & The experiment should measure ambient humidity outside. & R,T & Test 14 & To be done (earliest in July) & Pending \\
F.13. & The experiment shall send data via E-Link. & T & Test 13 & To be done (July) & Pending \\
F.14. & The experiment shall receive data via E-Link. & T & Test 13 & To be done (July) & Pending \\
P.1.1 & The \gls{ndir} sensor shall measure the concentration of methane with a range of 0.4 to 3.0 ppm. & R, T & Test 4, Test 14 & To be done (June) & Pending \\
P.1.2 & The \gls{ndir} sensor shall measure the concentration of methane with an uncertainty of 0.5 ppm or less. & R, T & Test 4, Test 14 & To be done (June) & Pending\\
P.2.1 & The \gls{ndir} sensor shall measure the concentration of carbondioxide with a range of 200 to 500 ppm. & R, T & Test 4, Test 14  & To be done (June) & Pending \\
P.2.2 & The \gls{ndir} sensor shall measure the concentration of carbondioxide with an uncertainty of 5 ppm or less. & R, T & Test 4, Test 14 & To be done (June) & Pending\\
P.3.1 & The \gls{ndir} sensor shall measure the concentration of water with a range of 1 to 30,000 ppm. & R, T & Test 4, Test 14  & To be done (June) & Pending \\
P.3.2 & The \gls{ndir} sensor shall measure the concentration of water with an uncertainty of 5 ppm or less. & R, T & Test 4, Test 14  & To be done (June) & Pending \\
P.4.1 & The pressure inside of the measurement chamber shall stay within a range of 2.5 and 3.2 bar.  & T & Test 2, Test 3, Test 5, Test 8 & To be done (earliest test in June) & Pending \\
P.4.2 & The pressure inside of the measurement chamber should stay within a range of 2.8 and 3 bar. & T & Test 3, Test 8 & To be done (earliest test in June) & Pending \\
P.5 & The pressurisation system shall have an air throughput of at least 0.4 l/min. & R, T & Test 3 & To be done (earliest test in June) & Pending \\
P.6.1 & The experiment shall measure the pressure inside of the measurement chamber in a range of 0.3 to 4.5 bar. & R, T & Test 3, Test 8 & To be done (June) & Pending \\
P.6.2 & The experiment shall measure the pressure inside of the measurement chamber with a maximum uncertainty of 0.02 bar. & R, T & Test 3, Test 8 & To be done (June) & Pending \\
P.7 & The temperature of the air inside of the measurement chamber shall stay within a range of 15 and 40\degree C while active. & A, T & Test 6, Test 9 & To be done (June)& Pending\\
P.8 & The temperature of the air inside of the measurement chamber should stay within a range of 19 and 24\degree C while active. & A, T & Test 6, Test 9 & To be done (June)& Pending \\
P.9.1 & The experiment shall measure the temperature inside of the measurement chamber in a range of -40 to +85 \degree C.  & R, T & Test 6, Test 9 & To be done (earliest test in June) & Pending \\
P.9.2 & The experiment shall measure the temperature inside of the measurement chamber with a maximum uncertainty of 1.5\degree C. & R, T & Test 6, Test 9 & To be done (earliest test in June) & Pending \\
P.10 & The experiment shall keep the humidity inside of the measurement chamber below 90\% r.H. & T & Test 13 & To be done (earliest test in July) & Pending \\
P.11.1 & The experiment shall measure the humidity inside of the measurement chamber in a range of 0 to 100\% r.H. & R, T & Test 4, Test 13, Test 14 & To be done (earliest test in June) & Pending \\
P.11.2 & The experiment shall measure the humidity inside of the measurement chamber with a maximum uncertainty of 3\% r.H. & R, T & Test 4, Test 14 & To be done (earliest test in June) & Pending \\

P.12 & The experiment should measure the temperature, pressure and humidity inside of the measurement chamber at a rate over 10 Hz. & R, T & Test 13, Test 15 & To be done (earliest test in July) & Pending \\
P.13.1 & The temperature in the electronic compartment shall stay within a range
of -25 and 85°C. & A,T & Test 6, Test 9 & To be done (July) & Pending  \\
P.13.2 & The temperature in the electronic compartment should stay within a range of -15 and 60°C. & A,T & Test 6, Test 9 & To be done (July) & Pending\\
P.14.1 & The experiment should measure the ambient pressure outside in a range of 20 to 1100 mbar. & R, T & Test 8 & To be done (July) & Pending \\
P.14.2 & The experiment should measure the ambient pressure outside with a maximum uncertainty of 20 mbar. & R, T & Test 14 & To be done (August) & Pending  \\
P.15.1 & The experiment should measure the ambient temperature outside in a range of -70 to +60 \degree C. & R, T & Test 9 & To be done (July) & Pending \\
P.15.2 & The experiment should measure the ambient temperature outside with a maximum uncertainty of 1.5\degree C. & R, T & Test 14 & To be done (August) & Pending \\
P.16.1 & The experiment should measure the ambient humidity outside in a range of 0 to 100\% r.H. & R, T & Test 14 & To be done (August) & Pending \\
P.16.2 & The experiment should measure the ambient humidity outside with a maximum uncertainty of 3\% r.H. & R, T & Test 13, Test 14 & To be done (August) & Pending \\
P.17 & The experiment should measure the ambient temperature, pressure and humidity outside at a rate over 10 Hz. & R, T & Test 13, Test 15 & To be done (earliest test in July) & Pending \\
P.18.1 & The experiment shall operate in the shock profile of the BEXUS vehicle flight and launch.& T & Test 7, Test 12 & To be done (earliest test in June) & Pending  \\
P.18.2 & The \gls{ndir} sensor should withstand the shocks of the landing. & T & Test 12 & To be done (July) & Pending \\
P.19 & The data storage shall be able to store at least 2GB. & R, T& Test 15 & To be done (August) & Pending\\
P.20 & The experiment should receive data via E-Link with an uplink rate under 10 kbps. & R, T & Test 13, Test 15 & To be done (earlist test in July) & Pending \\
P.21 & The experiment shall send the obtained data with the E-Link with a downlink rate under 100 kbps. & R, T & Test 13, Test 15 & To be done (earlist test in July)& Pending \\

D.1 & The experiment shall operate in the temperature profile of the BEXUS vehicle flight and launch. & A, T & Test 9 & To be done (July) & Pending \\
D.2.1 & The experiment shall operate in the pressure profile of the BEXUS vehicle flight and launch. & A, T & Test 1, Test 3, Test 8 & Test 1 completed successfully  & Pending \\
D.2.2 & The measurement chamber shall withstand a pressure difference of up to 4.5 bar.  & A, T & Test 8 & To be done (July) & Pending \\
D.3 & The experiment shall operate in the vibration profile of the BEXUS vehicle flight and launch. & T & Test 11 & To be done (July) & Pending \\
D.4 & The experiment power connector shall be an Amphenol PT02E8-4P, Code A. & R & & & \\
D.5 & The experiment data connector shall be an Amphenol RJF21B connector.  & R & & & \\
D.6 & The experiment shall not disturb or harm the launch vehicle.  & R, A, T & Test 2, Test 7, Test 11 & To be done (earlist test in June) & Pending \\
D.7 & The experiment shall consume less than 150 Wh during the flight. & T, A & Test 8, Test 9, Test 15 & To be done (earliest test in July) & Pending \\
D.8 & The experiment shall operate under 28.8\,V.  & R, T & Test 8, Test 9, Test 15 & To be done (earliest test in July) & Pending \\
D.9.1 & The experiment shall have no currents exceeding 2.4 A. & R, T & Test 8, Test 9, Test 15 & To be done (earliest test in July) & Pending \\
D.9.2 & The experiment should have no currents exceeding 1.4 A.  & R, T & Test 8, Test 9, Test 15 & To be done (earliest test in July) & Pending \\
D.10 & The experiment should stay within a size limit of 15x20x20 cm\textsuperscript{3}. & T & Test 10 & To be done (July) & Pending  \\
D.11 & The experiment shall stay within a weight limit of 5 kg. & A,T & Test 10 & To be done (July) & Pending \\
D.12 & The materials of the experiment shall not outgas. & R, T & Test 14 & To be done (August) & Pending \\

D.13 & The experiment shall have access to fresh air from outside. & R, I & & & \\
D.14 & The data storage shall be protected from water due to condensation or during landing. & R & & & \\
D.15 & The budget for all components except the K96 sensor should stay below 2000\texteuro.  & R & & & \\


O.1 & The experiment shall be able to conduct measurements autonomously in case connection with the ground segment is lost. & T & Test 13, Test 15 & To be done (earliest test in July) & Pending \\
O.2 & The experiment shall accept a request for radio silence at any time while on the launch pad.  & T & Test 13, Test 15 & To be done (earliest test in July) & Pending \\
O.3 & The experiment shall store all data on board and continuously send data to ground via E-Link.  & T & Test 13, Test 15 & To be done (earliest Test in July) & Pending \\
O.4 & The experiment shall automatically register and respond to high r.H. inside the chamber in order to lower the humidity. & T & Test 13 & To be done (July) & Pending \\

\end{longtable}

\clearpage
\section{Verification Plan}

All tests summarised in the tables below are explained in more detail in the test plan document on the Team Site. Including considerations about issues regarding the thermal tests.
%\begin{table}[htbp]
%\centering
%\caption{Controlled functionality testing and calibration of K96 sensor %only}
%\label{tab:test1}
%\begin{tabular}{L{5cm}L{10cm}}
%\toprule
%Test number & 1 \\
%Test type & Sensor functionality \\
%Test facility & Uppsala University \\
%Tested item & K96 sensor \\
%Model & Prototype Model \\
%Procedure, Test level and duration & Performance test, compare sensor %readings to known composition of gases tested with varying humidity %levels for measurement times of 20, 50 and 100s. \\
%Test campaign duration & 2 days \\
%Test campaign date & March \\
%Test completed & No \\
%Requirements verified & \\
%\bottomrule
%\end{tabular}
%\end{table}
\begin{table}[H]
\centering
\caption{Pressure test light bulb}
\label{tab:test_pressure_light_bulb}
\begin{tabular}{L{5cm}L{10cm}}
\toprule
Test number & 1 \\
Test type & Pressure test \\
Test facility & Uppsala University \\
Tested item & Light bulb of K96 sensor \\
Model & Prototype model \\
Procedure, Test level and duration & Put light bulb into airtight container and increase pressure slowly until at least 4.5 bar are reached or until the light bulb bursts. \\
Test campaign duration & 2 days \\
Test campaign date & March \\
Test completed & Yes \\
Requirements verified & Yes\\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\caption{Safety test for pressure vessel}
\label{tab:pressure_safety}
\begin{tabular}{L{5cm}L{10cm}}
\toprule
Test number & 2 \\
Test type & Pressure test \\
Test facility & Uppsala University, Vacuum chamber \\
Tested item & Measurement chamber without K96\\
Model & Prototype model \\
Procedure, Test level and duration & Pressurise the vessel to 4.5 bar and maintain that pressure for at least 10 hours in ambient conditions. Repeat this test in the vacuum chamber for 3 hours at approximately 5 mbar.  \\
Test campaign duration & 1 day \\
Test campaign date & June \\
Test completed & No \\
Requirements verified & \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\caption{Test of pressurisation system}
\label{tab:test_pressurisation_system}
\begin{tabular}{L{5cm}L{10cm}}
\toprule
Test number & 3 \\
Test type & Pressure test \\
Test facility & Uppsala University, Vacuum chamber \\
Tested item & Measurement chamber without K96\\
Model & Prototype model \\
Procedure, Test level and duration & Simulated Pressure Drop: Maintain 3 bar pressure over at least 5 minutes of stable operation with different degrees of inlet restriction to simulate different pressures. Monitor temperature of air and pumps during the test. \\
&Vacuum Chamber Test: Slowly lower the pressure from 1 bar to 10mbar and observe the stability of the 3 bar pressure inside the box. Setup as before but now data and power connection into Vacuum chamber. After continuous flow was validated, while at 10mbar, close the shutter and stop the pumps. Monitor if the pressure stays at 3 bar over at least 30 minutes to test for leaks.
  \\
Test campaign duration & 3 days \\
Test campaign date & June \\
Test completed & No \\
Requirements verified & \\
\bottomrule
\end{tabular}
\end{table}


\begin{table}[H]
\centering
\caption{Measurement chamber functionality}
\label{tab:test4}
\begin{tabular}{L{5cm}L{10cm}}
\toprule
Test number & 4 \\
Test type & Sensor functionality \\
Test facility & ICOS, Norunda \\
Tested item & Measurement Chamber \\
Model & Prototype Model \\
Procedure, Test level and duration & The K96 should be connected to a tube that gets air, which flows past the Picarro and if possible humidity, temperature and pressure sensors. To have some variability, the test should be run for at least 24 hours. \\
Test campaign duration & 2 days (setup and long term data collection) \\
Test campaign date & June \\
Test completed & No \\
Requirements verified & \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\caption{Outlet test}
\label{tab:test5}
\begin{tabular}{L{5cm}L{10cm}}
\toprule
Test number & 5 \\
Test type & Functionality test \\
Test facility & Uppsala University \\
Tested item & Outlet and shutter \\
Model & Prototype model \\
Procedure, Test level and duration & This test requires a heating plate with a pot of water or similar to vary humidity. The pressure chamber is pressurised to 3 bar with ambient air and the valve is opened. If there is no issue with freezing of the gas outlet after 5 minutes, the humidity is increased by increasing the water temperature and connecting the inlet to the air above the water. The relative humidity in the pressure chamber should be tracked to take note of the value from which freezing of the outlet becomes an issue. \\
Test campaign duration & 1 day \\
Test campaign date & June \\
Test completed & No \\
Requirements verified & \\
\bottomrule
\end{tabular}
\end{table}


\begin{table}[H]
\centering
\caption{Thermal control test}
\label{tab:test_thermal}
\begin{tabular}{L{5cm}L{10cm}}
\toprule
Test number & 6 \\
Test type & Thermal \\
Test facility & Uppsala University \\
Tested item & Thermal system \\
Model & Prototype model \\
Procedure, Test level and duration & Electronic Compartment test: Vary the ambient temperature down to at least -40°C (in thermal chamber or with dry ice) and use a heat pad and a temperature sensor to maintain the temperature of the PCB (or Arduino) within a target temperature range. Test also temperature resilience of SD Card if heating fails (if it works, switch it off towards the end and test if the SD card still has data and works). \\
& Air sample temperature control: Use the pressurization prototype and measurement chamber prototype (without K96 but with a temperature sensor) together with heating elements and temperature sensors at their corresponding places to test if and how well the air temperature can be controlled. Slowly lower the ambient temperature (in thermal chamber or using dry ice) while continuously pumping and measuring the temperature in the chamber. The goal is to maintain a temperature between 18 and 23°C inside of the measurement chamber even if ‘outside’ temperature is at least at -40°C.  \\
Test campaign duration & 3 days \\
Test campaign date & June \\
Test completed & No \\
Requirements verified & \\
\bottomrule
\end{tabular}
\end{table}




\begin{table}[H]
\centering
\caption{Static loads test}
\label{tab:test_static_loads}
\begin{tabular}{L{5cm}L{10cm}}
\toprule
Test number & 7 \\
Test type & Mechanical test \\
Test facility & Uppsala University \\
Tested item & Main structure of experiment \\
Model & Qualification model \\
Procedure, Test level and duration & Simulate mounting of the experiment on the gondola. Load the main structure with 10 to 30 times its own weight. \\
Test campaign duration & 1 day \\
Test campaign date & June (latest July) \\
Test completed & No \\
Requirements verified & \\
\bottomrule
\end{tabular}
\end{table}



\begin{table}[H]
\centering
\caption{Vacuum test of whole experiment}
\label{tab:vacuum_test}
\begin{tabular}{L{5cm}L{10cm}}
\toprule
Test number & 8  \\
Test type & Pressure test \\
Test facility & Uppsala University, Vacuum chamber \\
Tested item & Whole experiment \\
Model & Protoflight model \\
Procedure, Test level and duration & Come as close to rate of pressure decrease during balloon flight as possible. Monitor temperature, especially at sensitive components. Monitor pressure stability in measurement chamber. Lower the pressure down to 10 mbar and keep it there for an extended time (TBD) to observe the temperature change and make sure that the pressure is stable. \\
Test campaign duration & 2 days (setup and execution) \\
Test campaign date & July \\
Test completed & No \\
Requirements verified & \\
\bottomrule
\end{tabular}
\end{table}


\begin{table}[H]
\centering
\caption{Temperature test of whole experiment}
\label{tab:test_temperature}
\begin{tabular}{L{5cm}L{10cm}}
\toprule
Test number & 9 \\
Test type & Thermal \\
Test facility & Uppsala University \\
Tested item & Whole experiment \\
Model & Proto flight model \\
Procedure, Test level and duration & Put the fully assembled experiment into an environment that can vary the temperature from 10°C to at least -40°C. Try to simulate the rate of decrease according to the real conditions during ascent (challenging if we don’t get access to thermal chamber). Monitor functionality and temperature of pumps, air temperature in measurement chamber and temperature of electronics. \\
Test campaign duration & 3 days (1 day build-up, 2 day testing and packing) \\
Test campaign date & July \\
Test completed & No \\
Requirements verified & \\
\bottomrule
\end{tabular}
\end{table}


\begin{table}[H]
\centering
\caption{Weight and dimensions test}
\label{tab:weight_test}
\begin{tabular}{L{5cm}L{10cm}}
\toprule
Test number & 10 \\
Test type & Mechanical \\
Test facility & Uppsala University \\
Tested item & Whole experiment \\
Model & Qualification model \\
Procedure, Test level and duration & Measure outer dimensions. Put experiment on a scale. \\
Test campaign duration & 0.5 days \\
Test campaign date & July \\
Test completed & No \\
Requirements verified & \\
\bottomrule
\end{tabular}
\end{table}


\begin{table}[H]
\centering
\caption{Vibration test}
\label{tab:test_vibration}
\begin{tabular}{L{5cm}L{10cm}}
\toprule
Test number & 11 \\
Test type & Mechanical test \\
Test facility & Outside \\
Tested item & Whole experiment \\
Model & Qualification model \\
Procedure, Test level and duration & Mount experiment in the back of a car and drive through rough terrain, inspect condition of experiment afterwards and test full functionality of experiment. \\
Test campaign duration & 2 days \\
Test campaign date & July \\
Test completed & No \\
Requirements verified & \\
\bottomrule
\end{tabular}
\end{table}


\begin{table}[H]
\centering
\caption{Schock test}
\label{tab:test_shock}
\begin{tabular}{L{5cm}L{10cm}}
\toprule
Test number & 12 \\
Test type & Mechanical \\
Test facility & Uppsala University \\
Tested item & Whole experiment \\
Model & Qualification model \\
Procedure, Test level and duration & Drop experiment from 1 to 3 meters onto a padded surface and check visually and for full functionality afterwards. \\
Test campaign duration & 1 day \\
Test campaign date & July \\
Test completed & No \\
Requirements verified & \\
\bottomrule
\end{tabular}
\end{table}


\begin{table}[H]
\centering
\caption{Software testing}
\label{tab:test13}
\begin{tabular}{L{5cm}L{10cm}}
\toprule
Test number & 13 \\
Test type & Software test \\
Test facility & Uppsala University \\
Tested item & E-link and software, measurement chamber \\
Model & Whole experiment \\
Procedure, Test level and duration & Test processes included in flow chart. Focus on manual commands and taking control from automatic mode as well as communication via E-Link. Test data storage, up- and downlink. Test reaction to increase of air humidity by providing water vapor at the air inlet.\\
Test campaign duration & 1 day \\
Test campaign date & July \\
Test completed & No \\
Requirements verified & \\
\bottomrule
\end{tabular}
\end{table}


\begin{table}[H]
\centering
\caption{Full referenced functionality test}
\label{tab:test14}
\begin{tabular}{L{5cm}L{10cm}}
\toprule
Test number & 14 \\
Test type & Full referenced functionality test \\
Test facility & ICOS, Norunda \\
Tested item & Whole Experiment \\
Model & Flight Model \\
Procedure, Test level and duration & Take the fully assembled experiment to the Norunda measurement station. Collect data from the experiment and the reference sensors from the weather station to compare and assess the measurement quality at ground level. This is to be done over an extended time frame of at least 24 hours. \\
Test campaign duration & 2 days (setup and long term data collection) \\
Test campaign date & August \\
Test completed & No \\
Requirements verified & \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\caption{Bench test}
\label{tab:test_bench}
\begin{tabular}{L{5cm}L{10cm}}
\toprule
Test number & 15 \\
Test type & Long term test \\
Test facility & Uppsala University \\
Tested item & Whole experiment \\
Model & Flight Model \\
Procedure, Test level and duration & Assemble as for flight and run through simulated countdown of about 2 hours. Run experiment for 6 hours simulating ascent, float and descent. Simulate E-link dropouts as well. Consider recovery time as well for at least 24 hours. (We could consider doing the bench test at Norunda and fuse it with Test 14) \\
Test campaign duration & 2 days \\
Test campaign date & August \\
Test completed & No \\
Requirements verified & \\
\bottomrule
\end{tabular}
\end{table}


% % ... Additional test tables would follow similarly ...

\section{Verification Results}


\begin{table}[htbp]
\centering
\caption{Example of a test result overview}
\label{tab:test_result}
\begin{tabular}{L{5cm}L{10cm}}
\toprule
\textbf{Verification number} & \\
\textbf{Type of test} & \\
\textbf{Facility} & \\
\textbf{Verified item} & \\
\textbf{Verification description} & \\
\textbf{Expected results} & \\
\textbf{Obtained Results} & \\
\textbf{Conclusions} & \\
\bottomrule
\end{tabular}
\end{table}
